Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-25 chSiGaps/AO_bondedSi.tex
append the full path to the tables for the Si Gaps paper
replace all subfigure commands with subfloat-- subfigure is not supported by this template

\input{tbls/tbl_experiments.tex}

\input{tbls/tbl_meshPatterns.tex}

@@

\input{tbls/tbl_cary5000Pars.tex}

@@

\input{tbls/tbl_DerivedGapSizes}

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{chSiGaps/figs/VG03_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG03 hole region}
		\label{figVG03_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{chSiGaps/figs/VG03_f100.pdf}
                \caption{Measured spectrum and fit of VG03 hole region}
                \label{figVG03_f100}
        \end{subfigure}
\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.\label{figVG03full} }
\end{figure}

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{chSiGaps/figs/VG03p2_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG03 petal region}
		\label{figVG03p2_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{chSiGaps/figs/VG03_f045.pdf}
                \caption{Measured spectrum and fit of VG03 petal region}
                \label{figVG03_f045}
        \end{subfigure}
\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. \label{figVG03part}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf}
        \caption{Illustration of VG09-12 sample transport accessory measurement positions. \label{figVG0912_STA_illus} }
    \end{subfigure}
    \begin{subfigure}[b]{0.65\textwidth}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf}
        \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh \label{figVG0912}}
    \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.\label{figVG12}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf}
        \caption{Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh}
	\label{VG0912_0gap_corner}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_0gap.pdf}
        \caption{Measured spectrum of VG09-12}
        \label{VG0912_0gap}
    \end{subfigure}
\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
\label{figVG12}}
\end{figure}

>>>>

\input{chSiGaps/tbls/tbl_experiments.tex}

\input{chSiGaps/tbls/tbl_meshPatterns.tex}

@@

\input{chSiGaps/tbls/tbl_cary5000Pars.tex}

@@

\input{chSiGaps/tbls/tbl_DerivedGapSizes}

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\label{figVG03_corner}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 hole region]{\label{figVG03_f100}}
    	\includegraphics[width=\textwidth]{chSiGaps/figs/VG03_f100.pdf}
	\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\label{figVG03p2_corner}}
    	\includegraphics[width=\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 petal region]{\label{figVG03_f045}}
    	\includegraphics[width=\textwidth]{chSiGaps/figs/VG03_f045.pdf}
	\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Illustration of VG09-12 sample transport accessory measurement positions.]{\label{figVG0912_STA_illus}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf}
    \subfloat[Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\label{figVG0912}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf}
	\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\label{VG0912_0gap_corner}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf}
    \subfloat[Measured spectrum of VG09-12]{\label{VG0912_0gap}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_0gap.pdf}
	\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12}}
\end{figure}
